---
title: "NICE Lab: R Learning Phase 3"
author: "Jocelyn Li"
date: "11/30/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) #TRUE setting will show both your code and the output
```

# Question 1
```{r q1}
library(psych)
library(summarytools)
library(dplyr)
library(ggplot2)
```

# Question 2
```{r q2}
eid_2016 <- read.csv("EID_Data_MCAE2016.csv")
dim(eid_2016)
names(eid_2016)
```
Notes: I manually imported the dataset and changed the name. That's my favorite way to do that.

# Question 3
```{r q3}
summarytools::freq(eid_2016)
summarytools::descr(eid_2016)
```

# Question 4
```{r q4}
eid2_2016 <- eid_2016 %>% 
  dplyr::mutate(swl_mean = (swl01+swl02+swl03+swl04+swl05)/5, 
                exploration_mean = (meim01+meim02+meim04+meim08+meim10)/5,
                commitment_mean = (meim03+meim05+meim06+meim07+meim09+meim11+meim12)/7)
eid_mean <- eid2_2016 %>%
  dplyr::select(swl_mean, exploration_mean, commitment_mean)
View(eid_mean)
summarytools::descr(eid_mean)
```

# Question 5
```{r q5}
eid_mean %>% psych::corr.test()
psych::corr.test(eid_mean$swl_mean,eid_mean$exploration_mean)
```

# Question 6
```{r q6}
mod_eid=lm(swl_mean~1+exploration_mean+commitment_mean, data = eid_mean)
summary(mod_eid)
confint(mod_eid)
```

# Question 7
```{r q7}
plot(swl_mean~exploration_mean, data = eid_mean, main = "scatterplot of exploration mean and satisfaction mean", xlab = "mean exploration of Multigroup Ethnic Identity Measure", ylab = "mean satisfaction with life" )
plot(swl_mean~commitment_mean, data = eid_mean, main = "scatterplot of commitment mean and satisfaction mean", xlab = "mean commitment of Multigroup Ethnic Identity Measure", ylab = "mean satisfaction with life" )
```

# Question 8
```{r q8}
t.test(exploration_mean ~ usborn, data = eid2_2016)
t.test(commitment_mean ~ usborn, data = eid2_2016)
t.test(swl_mean ~ usborn, data = eid2_2016)

t.test(exploration_mean ~ firstgen, data = eid2_2016)
t.test(commitment_mean ~ firstgen, data = eid2_2016)
t.test(swl_mean ~ firstgen, data = eid2_2016)
```

# Question 9
```{r q9}
#usborn and three variables 
bp_born_expl <- ggplot2::ggplot(eid2_2016, aes(usborn, exploration_mean)) +
  geom_boxplot()
bp_born_expl
bp_born_com <- ggplot2::ggplot(eid2_2016, aes(usborn, commitment_mean)) +
  geom_boxplot()
bp_born_com
bp_born_swl <- ggplot2::ggplot(eid2_2016, aes(usborn, swl_mean)) +
  geom_boxplot()
bp_born_swl

#firstgeneration and three variables 
bp_fg_expl <- ggplot2::ggplot(eid2_2016, aes(firstgen, exploration_mean)) +
  geom_boxplot()
bp_fg_expl
bp_fg_com <- ggplot2::ggplot(eid2_2016, aes(firstgen, commitment_mean)) +
  geom_boxplot()
bp_fg_com
bp_fg_swl <- ggplot2::ggplot(eid2_2016, aes(firstgen, swl_mean)) +
  geom_boxplot()
bp_fg_swl
```

# Question 10
```{r q10}
anova(lm(exploration_mean ~ firstgen*usborn, data=eid2_2016))
anova(lm(commitment_mean ~ firstgen*usborn, data=eid2_2016))
anova(lm(swl_mean ~ firstgen*usborn, data=eid2_2016))
```

# Question 11
```{r q11}
boxplot(exploration_mean ~ firstgen * usborn, data=eid2_2016)
boxplot(commitment_mean ~ firstgen * usborn, data=eid2_2016)
boxplot(swl_mean ~ firstgen * usborn, data=eid2_2016)
```
Notes: Practicing really help me understand more deeply rather than just going through tutorials does. I spent a lot of time exploring on the internet and searched for other examples to help me figure out what do those commend really mean. R markdown is a very cool tool, making things tidy and neat.