---
title: "NICE Lab: R Learning Phase 3"
author: "Your Name"
date: "10/27/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) #TRUE setting will show both your code and the output
```

INSTRUCTION [DELETE BEFORE SUBMITTING]: 

RMarkdown is a great way to combine (1) codes, (2) output and visualization, and (3) your own write-up of the results.

1. Put in the codes relevant to each question in the code chunk below (replace the current ##comment).

2a. Click on the green arrow on the top right of each code chunk to check your output for that chunk. 
  2b. Alternatively, you can run each individual line just like in an R script file.

3. After each code chunk, you can summarize the results in your own words or add any other writing as needed. 

4. At the end, click on "Knit" on the task bar. Et voila! Your own R-generated report.


# Question 1
```{r q1}
##delete this line and put your code here
```

[DELETE BEFORE SUBMITTING]: Here, after each code chunk, you can include your own write-up or interpretation of the output.

# Question 2
```{r q2}
##delete this line and put your code here
```

# Question 3
```{r q3}
##delete this line and put your code here
```

# Question 4
```{r q4}
##delete this line and put your code here
```

# Question 5
```{r q5}
##delete this line and put your code here
```

# Question 6
```{r q6}
##delete this line and put your code here
```

# Question 7
```{r q7}
##delete this line and put your code here
```

# Question 8
```{r q8}
##delete this line and put your code here
```

# Question 9
```{r q9}
##delete this line and put your code here
```

# Question 10
```{r q10}
##delete this line and put your code here
```

# Question 11
```{r q11}
##delete this line and put your code here
```
