---
title: 'NICE Lab: R Learning Phase 3'
author: "Wendy Schlinsog"
date: "11/1/2020"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) #TRUE setting will show both your code and the output
```

# Question 1
```{r q1}
library(psych)
library(summarytools)
library(dplyr)
library(ggplot2)
```

# Question 2
```{r q2}
MCA_dat<-read.csv(file="~/Desktop/EID_Data_MCAE2016 (3).csv")
View(MCA_dat)
```

# Question 3
```{r q3}
summarytools :: freq(MCA_dat)
summarytools :: descr(MCA_dat)
```
This code generated frequency and descriptive statistics of the data. 

# Question 4
```{r q4}
MCA_dat <- MCA_dat %>% 
  dplyr::mutate(swl_mean = (swl01+swl02+swl03+swl04+swl05)/5, 
                meim_exp_mean = (meim01+meim02+meim04+meim08+meim10)/5,
                meim_com_mean = (meim03+meim06+meim05+meim07+meim09+meim11+meim12)/7)

MCA_dat %>% dplyr :: select(swl_mean, meim_exp_mean, meim_com_mean) %>% summarytools::descr()
```
This code was used to store the data as new variables based on the scale scores of MEIM and SWL. It then calculated the descriptive statistics for these new variables.

# Question 5
```{r q5}
MCA_dat %>% dplyr::select (swl_mean, meim_exp_mean, meim_com_mean) %>% psych::corr.test()

MCA_dat.cor = cor(x = MCA_dat$swl_mean, y = MCA_dat$meim_exp_mean)
```
This code was used to create a correlation matrix of the three new variables. It appears that exploration and commitment have a higher correlation to each other (0.68) than either of them have to satisfaction with life. Commitment has a higher correlation (0.26) to satisfaction with life than exploration (0.15).

# Question 6
```{r q6}
model1 <- lm(swl_mean ~ meim_exp_mean + meim_com_mean, data = MCA_dat)
summary(model1)
confint(model1)
```
This code created a multiple regression analysis with the commitment and exploration predicting satisfaction with life. Exploration had a much smaller t-value than commitment. Exploration also had a negative t-value and commitment had a positive t-value. This code also created confidence intervals for the estimates. 

# Question 7
```{r q7}
meim_exp_scat <-ggplot2::ggplot(MCA_dat, aes(meim_exp_mean, swl_mean))
meim_exp_scat+
  geom_point()+
  labs(x = "meim_exp", y= "swl" )+
  geom_smooth (method = "lm", color = "#E69F00")

meim_com_scat <-ggplot2::ggplot(MCA_dat, aes(meim_com_mean, swl_mean))
meim_com_scat+
  geom_point()+
  labs(x = "meim_com", y= "swl" )+
  geom_smooth (method = "lm", color = "#E69F00")
```
This code created scatter plots of satisfaction with life and exploration as well as satisfaction with life and commitment.

# Question 8
```{r q8}
t.test(MCA_dat$meim_exp_mean ~ MCA_dat$firstgen)
t.test(MCA_dat$meim_exp_mean ~ MCA_dat$usborn)
t.test(MCA_dat$swl_mean ~ MCA_dat$firstgen)
t.test(MCA_dat$swl_mean ~ MCA_dat$usborn)
t.test(MCA_dat$meim_com_mean ~ MCA_dat$usborn)
t.test(MCA_dat$meim_com_mean ~ MCA_dat$firstgen)
```
This code created t-tests for the three variables created, exploration, commitment, and satisfaction with life, for Born in the US and First Generation College Student. The t-test of satisfaction with life for born in the US seems to be the only one that has a significant p-value of 0.01121.

# Question 9
```{r q9}
US_meim_exp <- ggplot2::ggplot(MCA_dat, aes (usborn, meim_exp_mean, fill=usborn))
US_meim_exp +
  geom_boxplot() +
  labs(x="US born", y="meim_exp")

US_meim_com <- ggplot2::ggplot(MCA_dat, aes (usborn, meim_com_mean, fill=usborn))
US_meim_com +
  geom_boxplot() +
  labs(x="US born", y="meim_com")

US_swl <- ggplot2::ggplot(MCA_dat, aes (usborn, swl_mean, fill=usborn))
US_swl +
  geom_boxplot() +
  labs(x="US born", y="swl")

first_meim_exp <- ggplot2::ggplot(MCA_dat, aes (firstgen, meim_exp_mean, fill=firstgen))
first_meim_exp +
  geom_boxplot() +
  labs(x="First Generation", y="meim_exp")

first_meim_com <- ggplot2::ggplot(MCA_dat, aes (firstgen, meim_com_mean, fill=firstgen))
first_meim_com +
  geom_boxplot() +
  labs(x="First Generation", y="meim_com")

first_swl <- ggplot2::ggplot(MCA_dat, aes (firstgen, swl_mean, fill=firstgen))
first_swl +
  geom_boxplot() +
  labs(x="First Generation", y="swl")

```
This code created box plots of the three variables, exploration, commitment, and satisfaction with life for first generation college students and born in the US. 

# Question 10
```{r q10}
meim_exp <- aov (meim_exp_mean ~ firstgen + usborn, data=MCA_dat)
summary(meim_exp)

meim_com <- aov (meim_com_mean ~ firstgen + usborn, data=MCA_dat)
summary(meim_com)

swl_anova <- aov (swl_mean ~ firstgen + usborn, data=MCA_dat)
summary(swl_anova)
```
This code ran a 2-way ANOVA for born in the US and first generation college student for the 3 variable scales. Satisfaction with life had a significant value for born in the US. All other values appeared to be insignificant. 

# Question 11
```{r q11}
exp_boxplot <- ggplot2::ggplot(MCA_dat, aes (firstgen, meim_exp_mean, fill=usborn))
exp_boxplot +
  geom_boxplot() 

com_boxplot <- ggplot2::ggplot(MCA_dat, aes (firstgen, meim_com_mean, fill=usborn))
com_boxplot +
  geom_boxplot() 

swl_boxplot <- ggplot2::ggplot(MCA_dat, aes (firstgen, swl_mean, fill=usborn))
swl_boxplot +
  geom_boxplot() 
```
This code created boxplots to show the three variable scales distributions for born in the us and first generation college students. 