---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(readr)
EID_Data_MCAE2016 <- read_csv("D:/Work/Psychology Research/NICE Lab/EID_Data_MCAE2016.csv")
```

## R Markdown

Note:
The dataset includes the following variables (20 in all): 1) a unique ID for each participant,
2) whether the participant was born in the U.S. (yes/no), 3) whether the participant was the
first in their family to attend college (yes/no), 4) the 12-item Multigroup Ethnic Identity
Measure (MEIM; Roberts et al., 1999), and 5) the 5-item Satisfaction with Life Scale (SWL;
Diener et al., 1999).

For the MEIM and SWL only the raw items are included, not scale scores. Scoring
instructions are included on the OSF page. There you will also find a codebook that
describes all variables and possible values, as well as a R script file that includes a key for
the exercises (but don’t look at that now!). So you now have a dataset and a description of
that dataset. You are ready to go. Follow the instructions below to do some basic data
wrangling, analyses, and plots.

```{r}



"Begin by installing (as needed) and loading the following packages: summarytools,
dplyr, psych, ggplot2. You will also see references below to “base R.” This means that
the function is built into R and does not require a specific package to run. That reminds
me of another law:
Fourth Law of Learning R: There is no “right” way to do anything in R. There are always
at least two—and sometimes many more—different packages that can perform the
same function.
Indeed, you could complete this lesson using an entirely different set of packages. Good
to know for now, and play around as you want, but if you are just getting started I
suggest using the ones I listed above (besides, I only made a key for using those
packages, so you can’t cheat if you use different ones)."

library(dplyr)
library(psych)
library(summarytools)
library(ggplot2)
library(car)
attach(EID_Data_MCAE2016)
```

```{r}

#Read in the raw .csv data file. Do some checks to make sure that everything looks as it should and that the data were read in properly.

##View(EID_Data_MCAE2016)

```

```{r}
#Get to know the basics of your data by using summarytools to examine the frequencies and descriptive statistics for all items.

##Frequence for entire dataset
freq(EID_Data_MCAE2016)

##Descriptive analysis for entire dataset
descr(EID_Data_MCAE2016)

```

```{r}
#Use dplyr to calculate scale scores for the MEIM and SWL according to the scoring instructions and store them as new variables in a new dataset. Use summarytools to check the descriptive statistics of the new variables.

##EID Exploration Score
EID_Data_MCAE2016$Meim_Exploration_Score <- (as.numeric((EID_Data_MCAE2016$meim01+EID_Data_MCAE2016$meim02+EID_Data_MCAE2016$meim04+EID_Data_MCAE2016$meim08+EID_Data_MCAE2016$meim10)/5,names="Meim_Exploration_Score"))

##EID Commitment Score
EID_Data_MCAE2016$Meim_Commitment_Score <- 
(as.numeric((EID_Data_MCAE2016$meim03+EID_Data_MCAE2016$meim05+EID_Data_MCAE2016$meim06+EID_Data_MCAE2016$meim07+EID_Data_MCAE2016$meim09+EID_Data_MCAE2016$meim11+EID_Data_MCAE2016$meim12)/7,names="Meim_Commitment_Score"))

##SWL
EID_Data_MCAE2016$SWL_Score <- (as.numeric((EID_Data_MCAE2016$swl01+EID_Data_MCAE2016$swl02+EID_Data_MCAE2016$swl03+EID_Data_MCAE2016$swl04+EID_Data_MCAE2016$swl05)/5,names="SWL_Score"))

##Descriptive analysis
descr(EID_Data_MCAE2016[c("Meim_Exploration_Score","Meim_Commitment_Score","SWL_Score")])

```

```{r}
#Use the psych package to create a correlation matrix consisting of the three scale scores. Then run a command to get only the correlation between MEIM exploration and SWL.

## 3 constructs combined
corPlot(EID_Data_MCAE2016[c("Meim_Exploration_Score","Meim_Commitment_Score","SWL_Score")])

## MEIM exploration and SWL
cor.plot(EID_Data_MCAE2016[c("Meim_Exploration_Score","SWL_Score")])
```

```{r}
#Run a multiple regression analysis in base R with the two MEIM subscales predicting SWL. Request confidence intervals for the estimates.

##Multi-regression MEIM_Commitment and MEIM_Exploration predict SWL
Multi_regression_model <- lm(EID_Data_MCAE2016$SWL_Score~EID_Data_MCAE2016$Meim_Commitment_Score+EID_Data_MCAE2016$Meim_Exploration_Score)
summary(Multi_regression_model)
```

```{r}
#Create two scatterplots using ggplot2, one for MEIM exploration and SWL and one for MEIM commitment and SWL. And labels to the axes, change the scales, and add a fit line.

##MEIM exploration and SWL
ggplot(EID_Data_MCAE2016, aes(x = EID_Data_MCAE2016$Meim_Exploration_Score,y = EID_Data_MCAE2016$SWL_Score),)+
  geom_point()+
  labs(x='MEIM_exploration_Score', y='SWL_Score',title = 'MEIM exploration and SWL')+
  geom_abline()

##MEIM commitment and SWL
ggplot(EID_Data_MCAE2016, aes(x = EID_Data_MCAE2016$Meim_Commitment_Score,y = EID_Data_MCAE2016$SWL_Score),)+
  geom_point()+
  labs(x='MEIM_Commitment_Score', y='SWL_Score',title = 'MEIM commitment and SWL')+
  geom_abline()

```

```{r}
#Run two sets of independent samples t-tests in base R on the three scales scores, one set for Born in the U.S and one set for First Generation College Student (so six t-tests total).

##Exploration_USborn
t.test(EID_Data_MCAE2016$Meim_Exploration_Score~EID_Data_MCAE2016$usborn,mu = 0,paired = FALSE,var.equal = FALSE,conf.level = 0.95)

##Commitment_USborn
t.test(EID_Data_MCAE2016$Meim_Commitment_Score~EID_Data_MCAE2016$usborn,mu = 0,paired = FALSE,var.equal = FALSE,conf.level = 0.95)

##SWL_USborn
t.test(EID_Data_MCAE2016$SWL_Score~EID_Data_MCAE2016$usborn,mu = 0,paired = FALSE,var.equal = FALSE,conf.level = 0.95)

##Exploration_FirstGen
t.test(EID_Data_MCAE2016$Meim_Exploration_Score~EID_Data_MCAE2016$firstgen,mu = 0,paired = FALSE,var.equal = FALSE,conf.level = 0.95)

##Commitment_FirstGen
t.test(EID_Data_MCAE2016$Meim_Commitment_Score~EID_Data_MCAE2016$firstgen,mu = 0,paired = FALSE,var.equal = FALSE,conf.level = 0.95)

##SWL_FirstGen
t.test(EID_Data_MCAE2016$SWL_Score~EID_Data_MCAE2016$firstgen,mu = 0,paired = FALSE,var.equal = FALSE,conf.level = 0.95)
```

```{r}
#Create boxplots using ggplot2 showing the three scale score distributions for Born in the U.S and First Generation College Student (so again, six plots).

##Exploration_USborn
ggplot(EID_Data_MCAE2016, aes(y = EID_Data_MCAE2016$Meim_Exploration_Score,x = EID_Data_MCAE2016$usborn),)+
  geom_boxplot()+
  labs(y='MEIM_exploration_Score', x='Whether born in the US')
  
##Commitment_USborn
ggplot(EID_Data_MCAE2016, aes(y = EID_Data_MCAE2016$Meim_Commitment_Score,x = EID_Data_MCAE2016$usborn),)+
  geom_boxplot()+
  labs(y='Meim_Commitment_Score', x='Whether born in the US')

##SWL_USborn
ggplot(EID_Data_MCAE2016, aes(y = EID_Data_MCAE2016$SWL_Score,x = EID_Data_MCAE2016$usborn),)+
  geom_boxplot()+
  labs(y='SWL_Score', x='Whether born in the US')

##Exploration_FirstGen
ggplot(EID_Data_MCAE2016, aes(y = EID_Data_MCAE2016$Meim_Exploration_Score,x = EID_Data_MCAE2016$firstgen),)+
  geom_boxplot()+
  labs(y='MEIM_exploration_Score', x='Whether is first generation student')

##Commitment_FirstGen
ggplot(EID_Data_MCAE2016, aes(y = EID_Data_MCAE2016$Meim_Commitment_Score,x = EID_Data_MCAE2016$firstgen),)+
  geom_boxplot()+
  labs(y='Meim_Commitment_Score', x='Whether is first generation student')

##SWL_FirstGen
ggplot(EID_Data_MCAE2016, aes(y = EID_Data_MCAE2016$SWL_Score,x = EID_Data_MCAE2016$firstgen),)+
  geom_boxplot()+
  labs(y='SWL_Score', x='Whether is first generation student')

```

```{r}
#Run a 2-way ANOVA in base R for Born in the U.S x First Generation College Student predicting the three scales scores (so three ANOVAs).

##ANOVA_Exploration_USborn$Firstgen
ANOVA_Exploration_USborn_Firstgen <- lm(Meim_Exploration_Score ~ usborn + firstgen,data = EID_Data_MCAE2016)
Anova(ANOVA_Exploration_USborn_Firstgen,type="II")

##ANOVA_Commitment_USborn$Firstgen
ANOVA_Commitment_USborn_Firstgen <- lm(Meim_Commitment_Score ~ usborn + firstgen,data = EID_Data_MCAE2016)
Anova(ANOVA_Commitment_USborn_Firstgen,type="II")

##ANOVA_SWL_USborn$Firstgen
ANOVA_SWL_USborn_Firstgen <- lm(SWL_Score ~ usborn * firstgen,data = EID_Data_MCAE2016)
Anova(ANOVA_SWL_USborn_Firstgen,type="III")

##post.hoc:
library("multcomp")
library("emmeans")
library("lsmeans")
library("multcompView")

post_hoc_SWL_USborn_Firstgen <- lsmeans(ANOVA_SWL_USborn_Firstgen, 
                                 pairwise ~ usborn * firstgen, 
                                 adjust= "tukey")
post_hoc_SWL_USborn_Firstgen


```

```{r}
#Create boxplots using ggplot2 showing the three scale score distributions for Born in the U.S x First Generation College Student (so this time only three plots!).

##Exploration_USborn$Firstgen
ggplot(aes(y=Meim_Exploration_Score, x=usborn, fill=firstgen), data= EID_Data_MCAE2016)+geom_boxplot()+theme_bw()

##Commitment_USborn$Firstgen
ggplot(aes(y=Meim_Commitment_Score, x=usborn, fill=firstgen), data= EID_Data_MCAE2016)+geom_boxplot()+theme_bw()

##SWL_USborn$Firstgen
ggplot(aes(y=SWL_Score, x=usborn, fill=firstgen), data= EID_Data_MCAE2016)+geom_boxplot()+theme_bw()

  

```

```{r}
#Write a summary report describing everything you did in steps 1-11, embedding figures and using APA style to report the results of your tests. Feel free to make tables as well.

```